The Atala PRISM Protocol

### 2022-11-22 prism-backend/research/prism-protocol/did_atala.tex
Working on DID proof.

\todo{Mention public delayed outputs.}

@@

    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
          \pccomment{\fbox{DID Create operation}} \\
          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
          \text{abort} \\
          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{CreateOk}, \sid, did,
          \lbrace (i, \val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (\cdot,\did,\cdot) \notin \DID: \\
          \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
          (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Created},\sid,\did,
          \lbrace (i,\val_i) \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \pccomment{\fbox{DID Read operation}} \\
          \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
          \pcif (\cdot,did,\sval) \in \DID: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,\sval))~\text{to}~P \\
          \pcelse: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,\bot)~\text{to}~P    
        }    
      \end{minipage}
    }
    \vspace*{0.25em} \\
    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{      
          \pccomment{\fbox{DID Update operation}} \\
          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
          \text{abort} \\
          \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{UpdateOk},\sid,
          \lbrace (i,\val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID: \\
          \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{7em} \lbrace (P, did,
          \lbrace (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Updated},\sid,
          (\did,\lbrace (i,\val_i) \rbrace_{i\in[n]}))
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
          \pccomment{\fbox{DID Deactivate operation}} \\
          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID~\land \\
          \pcind \lbrace (i,\lbl_i) \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
          \pcind \sval' \gets \sval \setminus \lbrace (i,\lbl_i,\cdot)
          \rbrace_{i\in[n]} \\
          \pcind \pcif \P(\sval') = 1: \\
          \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{8em}\lbrace (P,did,\sval') \rbrace \\
          \ucio{Output}~(\uccmd{Deacted},\sid,(\did,\sval'))
        }
      \end{minipage}
    }
  \end{framed}
  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID.}
  \label{fig:fpkidid}
\end{figure}

@@

\paragraph{DID Operations.} %
\todo{For now, this ignores \emph{unpublished} DIDs.}
\figref{fig:atalapkidid1} and \figref{fig:atalapkidid2} contain the
specification of Atala PRISM's DID method,
which we describe next. Looking at the \texttt{Create} and \texttt{Update}
operations, it is clear that $\P(\lbrace \lbl_i \rbrace_{i\in[n]})$ in Atala
requires that all key labels are of a known type (\MasterKey, \IssueKey,
\CommKey, or \AuthKey) and that at least one of the keys in the DID Document
is of type \MasterKey.

\begin{description}
\item{\uccmd{Create}.} %
  To create a DID, the user has to specify the key pairs to create, along with
  fresh identifiers and their type. For ease of exposition, we assume that the
  used identifiers just follow a sequence. The predicate \P in Atala simply
  requires that at least one key pair of \MasterKey type is created. The
  \uccmd{Create} algorithm creates as many keys of each type as requested,
  and keeps a list with the identifier, type and public key of each key pair.
  This list is then hashed into a value \texttt{h}, and the created DID is
  ``\texttt{\did:prism:h}''. A transaction containing the created list, the
  DID, and the \texttt{CreateDID} instruction is sent to the blockchain,
  signed by one of the master keys -- w.l.o.g., we simply use the first one
  in the list. The DID owner stores locally the list, along with the
  corresponding private keys.
\item[\uccmd{Read}.] %
  Getting the contents of a DID simply requires processing the associated
  transactions in the blockchain. Namely, transactions $(\tx,\sig)$ where $\tx$
  is either $(\texttt{CreateDID},\did,\cdot)$ or $(\texttt{UpdateDID},\did,
  \cdot)$. The associated DID Document is the result of applying in an ordered
  manner (from oldest to newest) all such validly signed transactions.
\item[\uccmd{Update}.] %
  Updating a DID requires to (optionally) specify a list of previously existing
  key identifiers to remove, and (optionally) specify a list of new key
  identifiers, and their types, to add. To simplify notation, we just adopt the
  (equivalent) convention that the caller indicates a list of $(i,\lbl_i)$
  pairs, which is interpreted as follows. If $i$ is an already existing
  identifier, the label is ignored and the corresponding key is not removed. If
  $i$ is a new identifier, then a new key pair of the given type is created.
  Omitting an existing identifier is then interpreted as the desire to remove
  the corresponding key pair. Otherwise, the same policy as for \uccmd{Create}
  applies here. Key pairs for the new keys are generated, and a transaction is
  sent to the blockchain, signed with one of the master keys in the DID
  \emph{before applying the update}. This transaction contains a list of the
  identifiers of the keys to remove, and a list of the identifiers and types
  of the keys to add.
\item[\uccmd{Deactivate}.] %
  A deactivate operation is simply an update operation with no new key
  identifiers, and that only specifies the existing identifiers that will
  \emph{not} be deactivated.
\end{description}

@@

\begin{figure}[ht!]
  \begin{framed}
    \scalebox{0.9}{
      \begin{minipage}[t]{\textwidth}
        \textrm{Party $P$ running operation \cmd with arguments \arg, in
          session \sid.} \\
        \textrm{We assume that the party running
          \texttt{Update} and \texttt{Deactivate} operations has an up to date
          copy $(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$ of the DID to
          modify. Otherwise, a \texttt{Read} operation needs to be run before.}
      \end{minipage}
    }
    \vspace*{0.5em}

    \scalebox{0.90}{          
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in\tilde{N}\subseteq [\tilde{n}]})$}{
          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
          \CommKey,\IssueKey] \lor
          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
          \pcind \texttt{abort} \\
          \st_{add} \gets \emptyset \\
          \pcfor i \in \tilde{N}~\suchthat~ i > n : \\
          \pcind \ucsend~(\uccmd{KeyGen},((P,i),\sid))~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},((P,i),\sid),\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st_{add} \gets \st_{add} \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
          \st_{del} \gets [n] \setminus \tilde{N} \\
          % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
          \tx \gets (\texttt{UpdateDID}, \did, (\st_{del}, \st_{add})) \\
          j \gets \LMKI(\lbrace \lbl_i \rbrace_{i\in\tilde{N}}) \\
          \ucsend~(\uccmd{Sign},((P,j),\sid),\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},((P,j),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
          \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.45\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in N \subseteq[n]})$}{       
          \text{Run as a \texttt{Update} operation}
        }
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
  \label{fig:atalapkidid2}
\end{figure}

@@

\todo{Define $\P_{Atala}$}

@@

\begin{proof}
  We show that \RealPKIDIDAtala UC-realizes \IdealFPKIDID, when configured
  with policy $\P_{Atala}$. For this, we give a simulator \Sim such that, for
  any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
  \Exec_{\phiDIDAtala,\Sim,\Env}$,
  where \phiDIDAtala is a protocol composed with the same parties as
  \RealPKIDIDAtala but where each party is simply a dummy party that forwards
  any incoming/outgoing message to the ideal functionality \IdealFPKIDID. The
  simulator \Sim runs internally a copy of the real-world adversary \adv, as
  well as the ideal functionalities \IdealFRO, \IdealFSig and \IdealFaobb,
  and any involved party.

  \begin{description}
  \item[Simulating DID Create.] %
    %
    % Policy check
    \todo{Policy check not needed by \Sim, right?}
    When \Sim receives a message $(\uccmd{Create},\sid,\lbrace (i,\lbl_i)
    \rbrace_{i\in[n]})$ from a (dummy) party $P$, it simulates for \adv~the key
    generation process of $n$ signing key pairs, by sending $n$
    $(\uccmd{KeyGen},((P,i),\sid))$ queries to \adv~on
    behalf of \IdealFSig, and receiving the $n$ corresponding $(\uccmd{VerKey},
    ((P,i),\sid),\pk_i)$ responses.
    %
    % Hash computation
    \Sim then concatenates all $(i,\lbl_i,\pk_i)$ tuples into \st, and simulates
    a query to \IdealFRO \todo{do we need programmability or something?}, to set
    \did as ``$did:prism: h$'' as DID value.
    %
    % Tx sim
    With the DID value, \Sim simulates for \adv~the preparation of transaction
    \tx. That is, \Sim uses the master key with lower index, $j \gets
    \LMKI(\st)$, and simulates a query $(\uccmd{Sign},((P,j),\sid),\tx)$ to
    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,j),\sid),\tx,\sig)$.
    %
    % BB append
    \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealFaobb.
    %
    % Output
    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace (i,\pk_i)
    \rbrace_{i\in[n]})$ to \IdealFPKIDID.
    Note that \did is generated uniformly at random. Thus, the probability that
    \IdealFPKIDID halts because $\did \in \DID$ is negligible, and \IdealFPKIDID
    outputs $(\uccmd{Created},\sid,\did,\lbrace (i,\val_i) \rbrace_{i\in[n]})$
    to \Sim.
  \item[Simulating DID Read.]
  \item[Simulating DID Update.] 
  \item[Simulating DID Deactivate.] Directly follows from DID Update.      
  \end{description}
\end{proof}

>>>>

\todo{Syntax using counter indexes doesn't seem a good idea (the simplification
  does not seem to work for proving security). Maybe change to arbitrary labels
  (and change current key label name to key type).}
\todo{Mention public delayed outputs.}
\todo{If the functionality tries to fetch some entry from a list, and the entry
  does not exist, then it aborts (assumed for updates).}

@@

    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
          \pccomment{\fbox{DID Create operation}} \\
          \pcif \P(\lbrace (\lbl_i, \typ_i) \rbrace_{i\in[n]}) = 0:
          \text{abort} \\
          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{CreateOk}, \sid, did,
          \lbrace (\lbl_i, \val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (\cdot,\did,\cdot) \notin \DID: \\
          \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
          (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Created},\sid,\did,
          \lbrace (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \pccomment{\fbox{DID Read operation}} \\
          \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
          \pcif (\cdot,did,\sval) \in \DID: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,\sval))~\text{to}~P \\
          \pcelse: \\
          \pcind \ucio{Output}~(\uccmd{Read},\sid,\bot)~\text{to}~P    
        }    
      \end{minipage}
    }
    \vspace*{0.25em} \\
    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[\tilde{n}]})$}{
          \pccomment{\fbox{DID Update operation}} \\
          % \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
          % \text{abort} \\
          \pcif (P,\did,\sval) \in DID: \\
          \pcind \sval_{del} \gets \sval \setminus
          \lbrace (\lbl_i,\cdot) \rbrace_{i\in[\tilde{n}]} \\ 
          \pcind \sval_{add} \gets \lbrace (\lbl_i,\typ_i)
          \rbrace_{i\in[\tilde{n}]} \setminus \sval_{del} \\
          \pccomment{\todo{Continue here!! XXXX}} \\
          \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{UpdateOk},\sid,
          \lbrace (i,\val_i) \rbrace_{i\in[n]}) \\
          \pcind \text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID:  \\
          \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{7em} \lbrace (P, did,
          \lbrace (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
          \ucio{Output}~(\uccmd{Updated},\sid,
          (\did,\lbrace (i,\val_i) \rbrace_{i\in[n]}))
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
          \pccomment{\fbox{DID Deactivate operation}} \\
          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
          \pcif (P,did,\sval) \in \DID~\land \\
          \pcind \lbrace (i,\lbl_i) \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
          \pcind \sval' \gets \sval \setminus \lbrace (i,\lbl_i,\cdot)
          \rbrace_{i\in[n]} \\
          \pcind \pcif \P(\sval') = 1: \\
          \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
          \hspace*{8em}\lbrace (P,did,\sval') \rbrace \\
          \ucio{Output}~(\uccmd{Deacted},\sid,(\did,\sval'))
        }
      \end{minipage}
    }
  \end{framed}
  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID.}
  \label{fig:fpkidid}
\end{figure}

@@

\paragraph{DID Operations.} %
\todo{For now, this ignores \emph{unpublished} DIDs.}
\figref{fig:atalapkidid1} and \figref{fig:atalapkidid2} contain the
specification of Atala PRISM's DID method,
which we describe next. Looking at the \texttt{Create} and \texttt{Update}
operations, it is clear that $\P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]})$ in
Atala requires that all key labels are of a known type (\MasterKey, \IssueKey,
\CommKey, or \AuthKey) and that at least one of the keys in the DID Document
is of type \MasterKey.

\begin{description}
\item{\uccmd{Create}.} %
  To create a DID, the user has to specify the key pairs to create, along with
  fresh identifiers and their type. For ease of exposition, we assume that the
  used identifiers just follow a sequence. The predicate \P in Atala simply
  requires that at least one key pair of \MasterKey type is created. The
  \uccmd{Create} algorithm creates as many keys of each type as requested,
  and keeps a list with the identifier, type and public key of each key pair.
  This list is then hashed into a value \texttt{h}, and the created DID is
  ``\texttt{\did:prism:h}''. A transaction containing the created list, the
  DID, and the \texttt{CreateDID} instruction is sent to the blockchain,
  signed by one of the master keys -- w.l.o.g., we simply use the first one
  in the list. The DID owner stores locally the list, along with the
  corresponding private keys.
\item[\uccmd{Read}.] %
  Getting the contents of a DID simply requires processing the associated
  transactions in the blockchain. Namely, transactions $(\tx,\sig)$ where $\tx$
  is either $(\texttt{CreateDID},\did,\cdot)$ or $(\texttt{UpdateDID},\did,
  \cdot)$. The associated DID Document is the result of applying in an ordered
  manner (from oldest to newest) all such validly signed transactions.
\item[\uccmd{Update}.] %
  To update a DID, we first assume for ease of exposition that the calling party
  $P$ has an updated version of the associated DID Document (which included
  a list of $n$ keys) -- if this is not the case, it suffices to make first a
  call to \uccmd{Read} for the given DID. \todo{This seems relevant enough to
    be highlighted in some more visible place, no?}
  Then, updating a DID requires to (optionally) specify a list of previously
  existing key identifiers to remove, and (optionally) specify a list of new key
  identifiers, and their types, to add. To simplify notation, we just adopt the
  (equivalent) convention that the caller indicates a list of $\lbrace (i,
  \lbl_i) \rbrace_{i\in\tilde{N}\subseteq[\tilde{n}]}$ pairs, where $\tilde{n}$
  may be smaller or larger than $n$, depending on the desired update. This
  list is then interpreted as follows. If $i$ is an already existing
  identifier, the label is ignored and the corresponding key is not removed. If
  $i$ is a new identifier, then a new key pair of the given type is created.
  Omitting an existing identifier is then interpreted as the desire to remove
  the corresponding key pair. Otherwise, the same policy as for \uccmd{Create}
  applies here. Key pairs for the new keys are generated, and a transaction is
  sent to the blockchain, signed with one of the master keys in the DID
  \emph{before applying the update}. This transaction contains a list of the
  identifiers of the keys to remove, and a list of the identifiers and types
  of the keys to add.
\item[\uccmd{Deactivate}.] %
  A deactivate operation is simply an update operation with no new key
  identifiers, and that only specifies the existing identifiers that will
  \emph{not} be deactivated.
\end{description}

@@

\begin{figure}[ht!]
  \begin{framed}
    \scalebox{0.9}{
      \begin{minipage}[t]{\textwidth}
        \textrm{Party $P$ running operation \cmd with arguments \arg, in
          session \sid.} \\
        \textrm{We assume that the party running
          \texttt{Update} and \texttt{Deactivate} operations has an up to date
          copy $(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$ of the DID to
          modify. Otherwise, a \texttt{Read} operation needs to be run before.
          If no such \did exists, the execution is aborted.}
      \end{minipage}
    }
    \vspace*{0.5em}

    \scalebox{0.90}{          
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in\tilde{N}\subseteq [\tilde{n}]})$}{
          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
          \CommKey,\IssueKey] \lor
          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
          \pcind \texttt{abort} \\
          \st_{add} \gets \emptyset \\
          \pcfor i \in \tilde{N}~\suchthat~ i > n : \pccomment{$n$ is determined
            by the local $(\did, \lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$
            copy}\\
          \pcind \ucsend~(\uccmd{KeyGen},((P,i),\sid))~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},((P,i),\sid),\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st_{add} \gets \st_{add} \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
          \st_{del} \gets [n] \setminus \tilde{N} \\
          % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
          \tx \gets (\texttt{UpdateDID}, \did, (\st_{del}, \st_{add})) \\
          j \gets \LMKI(\lbrace \lbl_i \rbrace_{i\in\tilde{N}}) \\
          \ucsend~(\uccmd{Sign},((P,j),\sid),\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},((P,j),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
          \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.45\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \lbrace (i,\lbl_i) \rbrace_{i\in N \subseteq[n]})$}{       
          \text{Run as a \texttt{Update} operation}
        }
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
  \label{fig:atalapkidid2}
\end{figure}

@@

Before going into the proofs, observe that the \uccmd{Create} and \uccmd{Update}
operations in \RealPKIDIDAtala include (in lines 1-2) a policy on the received
indexes and labels. Concretely, this policy requires that all labels are of a
known key type, and that at least one of them is of type \MasterKey. In the
sequel, we use $\P_{Atala}$ to refer to this policy.

@@

\begin{proof}
  We show that \RealPKIDIDAtala UC-realizes \IdealFPKIDID, when configured
  with policy $\P_{Atala}$. For this, we give a simulator \Sim such that, for
  any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
  \Exec_{\phiDIDAtala,\Sim,\Env}$,
  where \phiDIDAtala is a protocol composed with the same parties as
  \RealPKIDIDAtala but where each party is simply a dummy party that forwards
  every message from \Env to the ideal functionality \IdealFPKIDID, and every
  response from \IdealFPKIDID back to \Env. The simulator \Sim runs internally a
  copy of the real-world adversary \adv, as well as the ideal functionalities
  \IdealFRO, \IdealFSig and \IdealFaobb, and any involved party.

  \begin{description}
  \item[Simulating DID Create.] %
    % 
    % Policy check
    First, note that \IdealFPKIDID is parameterised with $\P_{Atala}$. Thus,
    if the input labels don't match the policy, the functionality rejects the
    request, just as in the real protocol \RealPKIDIDAtala.
    %
    % Keys generation
    Next, when \Sim receives a message $(\uccmd{Create},\sid,\lbrace (i,\lbl_i)
    \rbrace_{i\in[n]})$ from (dummy) party $P$, it simulates for \adv~the key
    generation process of $n$ signing key pairs, by sending $n$
    $(\uccmd{KeyGen},((P,i),\sid))$ queries to \adv~on
    behalf of \IdealFSig, and receiving the $n$ corresponding $(\uccmd{VerKey}, 
    ((P,i), \sid), \pk_i)$ responses.
    %
    % Hash computation
    \Sim then concatenates all $(i,\lbl_i,\pk_i)$ tuples into \st, and simulates
    a query to \IdealFRO \todo{do we need programmability or something?}, to set
    \did as ``$did:prism: h$'' as DID value.
    %
    % Tx sim
    With the DID value, \Sim simulates for \adv~the preparation of transaction
    \tx. That is, \Sim uses the master key with lower index, $j \gets
    \LMKI(\st)$, and simulates a query $(\uccmd{Sign},((P,j),\sid),\tx)$ to
    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,j),\sid),\tx,\sig)$.
    %
    % BB append
    \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealFaobb.
    %
    % Output
    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace (i,\pk_i)
    \rbrace_{i\in[n]})$ to \IdealFPKIDID, and stores the tuple $(\did,\lbrace
    (i,\lbl_i,\pk_i)\rbrace_{i\in[n]})$.
    Note that \did is generated by an ideal random oracle (thus, uniformly at
    random), just as in the real protocol \RealPKIDIDAtala. Thus, the
    probability that \IdealFPKIDID halts because $\did \in \DID$ is negligible,
    and \IdealFPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace (i,\val_i)
    \rbrace_{i\in[n]})$.
  \item[Simulating DID Read.]
    %
    % Ack
    Upon receiving $(\uccmd{Read},\sid,\did)$ from dummy party P, \Sim simply
    forwards the message to \adv and waits until receiving the response, which
    is forwareded back to P.
    %
    % Consistent and indistinguishable results
    Now, we show that the value returned by \IdealFPKIDID is indistinguishable
    to that of \RealPKIDIDAtala. \todo{Do after Update.}
  \item[Simulating DID Update.]
    % 
    % Policy check
    First, note that \IdealFPKIDID is parameterised with $\P_{Atala}$. Thus,
    if the input labels don't match the policy, the functionality rejects the
    request, just as in the real protocol \RealPKIDIDAtala.
    % 
    % Read if needed
    First, \Sim finds in its records the entry $(\did,\lbrace (i,\lbl_i,\pk_i)
    \rbrace_{i\in[n]})$. If no such \did exists, aborts.
    %
    % Simulate generation of new keys
    Then, \Sim parses the $\lbrace(i,\lbl_i)\rbrace_{i\in\tilde{N}\subseteq
      [\tilde{n}]}$ for new indexes, and simulates for \adv~one call to the
    $\uccmd{KeyGen}$ interface of \IdealFSig for each new key, and composes the
    variable $\st_{add}$ as in the real protocol. Similarly, \Sim initializes
    variable $\st_{del}$ by looking for indexes in $[n]$ no longer present in
    $\tilde{N}$.
    %
    % Simulate transaction
    Finally, \Sim prepares the transaction \tx as in the real protocol using
    variables $\st_{add}$ and $\st_{del}$. For this, a \uccmd{Sign} request is
    sent to \IdealFSign, and an \uccmd{Append} request is sent to \IdealFaobb.
    \Sim sends the resulting $(\uccmd{UpdateOK},\sid,\lbrace (i,\pk_i)
    \rbrace_{i\in[\tilde{N}]})$ back to \IdealFPKIDID.
    %
    % Indistinguishability
    Note that, if \Sim does not abort, then a valid $(P,\did,\sval)$ entry must
    exist in the \DID state variable of \IdealFPKIDID. Thus, \IdealFPKIDID does
    not abort in line 6. Then, \IdealFPKIDID
  \item[Simulating DID Deactivate.] Directly follows from DID Update.      
  \end{description}
\end{proof}
